```
title: Appendix 

```

```{r}

matchIdx = function(filename,numIdx){#the file contain three columns 'medallion', 'hack_license' and 'pickup_datatime'
  
  nrows = system(sprintf('wc -l %s', paste(filename, collapse = ' ')), intern = TRUE)
  
  idx = sample(nrows,numIdx)
  
  idx = sort(idx)
  
  write.table(idx,'matchidx.txt',quote = FALSE,row.names = FALSE,col.names = FALSE)
}

# USE SEHLL cat matchidx.txt | ./sample datamatch.txt > tripdata.txt

# USE SEHLL cat matchidx.txt | ./sample farematch.txt > tripfare.txt

match_test = function(tripdata,tripfare){
  
  data = data.table:::fread(tripdata,header = FALSE)
  
  fare = data.table:::fread(tripfare,header = FALSE)
  
  if ( any(data$V1 != fare$V1) | any(data$V2 != fare$V2) | any(data$V3 != data$V3) ){
    
    
    print('trip_data and trip_fare are not matched')
    
  } else {
    
    print('trip_data and trip_fare are matched')
    
  }
  
}






```



1.First method in problem 1
```{r}
g = function(filename){
   t = fread(filename,header = FALSE)#numeric
   
   q = quantile(t$V1,prob = seq(0,1,0.1))
   
   q 
  }

```

2.Second method in problem 1
```{r}

getTable = function(){

f = list.files("/home/data/NYCTaxis", pattern = "fare.*\\.csv$", full.names = TRUE)

cl = makeCluster(12, 'FORK')

els = clusterSplit(cl, f)

wc = clusterApply(cl,els,function(x) table(as.numeric(system(sprintf("awk -F ',' 'FNR > 1 { print $11 - $10 }' %s", paste(x, collapse = ' ')),intern = TRUE))))

stopCluster(cl)

wc = unlist(wc)

nrows = max(cumsum(wc))

wc = tapply(as.numeric(wc), factor(names(wc)),sum)# nerge tables

name = as.numeric(names(wc))

j = match(name, sort(name))

wc = wc[j]

idx = c(seq(from = 1,to = nrows,by = nrows/10),nrows)

quant = vector(mode = 'numeric', length = 10)

for(i in 1:10){
  
  quant[i] = wc[ max(cumsum(cumsum(wc) <= idx[i])) ]
  
}

names(quant) = c('0%','10%','20%','30%','40%','50%','60%','70%','80%','90%','100%')

quant
}


```



2.Simple linear
```{r}
l = function(x){

x = data.table:::fread('finallytime.txt',header = FALSE)

y = data.table:::fread('finallydiff.txt',header = FALSE)

con = cov(x$V1,y$V1)

d = sd(x$V1)

beta1 = con/(d^2)

x_bar = mean(x$V1)

y_bar = mean(y$V1)

beta0 = y_bar - beta1*x_bar

c(beta0,beta1)

y_fit = beta0 + beta1*x

MSE = sum((y-y_fit)^2)/173176144

list(coefficent = c(beta0,beta1), MSE = MSE, residual = y - y_fit)
}
```


3.multiple Regression
```{r}
function(){

  x = read.big.matrix('nominus.txt', sep = '\t') # nominus.txt has surcharge, triptime,and #totallesstoll.

beta = solve(t(x[,1:2])%*%x[,1:2])%*%t(x[,1:2])%*%x[,3]

intercept = mean(x[,3]) - beta[1]*mean(x[,1]) - beta[2]*mean(x[,2])

beta0 = intercept

beta1 = beta[1]

beta2 = beta[2]

y_fit = beta0 + beta1*x[,1] + beta2*x[,2]

residual = x[,3] - y_fit

MSE = sum((x[,3]-y_fit)^2)/173176144

list(coefficent = c(beta0,beta1,beta2), MSE = MSE, residual = residual)

}